---
title: "test"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Frame 

This report is for finding the state which holds the highest sale of onions 
Predict the price of onion for the next few mont  hs for that state.
Some of the cities don't have the state appended to it, it will be modified 
while cleaning the data.

# Acquire data

The data was acquired from NHDRF site using the date wise arrival for the year 2017


```{r AcquireData}
library(rvest)
dateWiseArrival = read_html("DateWiseMA2017_Onion.html")
dateWiseTable = dateWiseArrival %>% 
            html_node('#dnn_ctr966_DailyWiseMarketArrivals_GridView1') %>%
            html_table()
tempDateWiseTable = dateWiseTable
str(dateWiseTable)
```

# Refine Data
- adding state to cities which dont have the state .This is to get the accurate results  
- Remove the last row
- Rename the columns 
- Change data types
- Create a date column 
- Clean up City Name
-
```{r Refine}


library(tidyr)

library(stringr)


library(dplyr)
colnames(dateWiseTable)= c("DOA","Market","Arrival","MinPrice","MaxPrice","Price")


dateWiseTable = dateWiseTable %>% filter( Market != "Total")




dateWiseTable$MinPrice=as.numeric(dateWiseTable$MinPrice)
dateWiseTable$MaxPrice=as.numeric(dateWiseTable$MaxPrice)
dateWiseTable$Price=as.numeric(dateWiseTable$Price)
dateWiseTable$NewDOA=as.Date(dateWiseTable$DOA,"%d/%B/%Y")

levels(dateWiseTable$Market)= NULL
dateWiseTable$Market =dateWiseTable$Market %>% str_replace("\\(Podis","")

dateWiseTable$Market =dateWiseTable$Market %>% str_replace("BANGALORE","BANGALORE(KNT)")
dateWiseTable$Market =dateWiseTable$Market %>% str_replace("CHENNAI","CHENNAI(TN)")
dateWiseTable$Market =dateWiseTable$Market %>% str_replace("DELHI","DELHI(DEL)")
dateWiseTable$Market =dateWiseTable$Market %>% str_replace("MUMBAI","MUMBAI(MS)")
dateWiseTable$Market =dateWiseTable$Market %>% str_replace("HYDERABAD","HYDERABAD(TELANGANA)")

dateWiseTable$Market =dateWiseTable$Market %>% str_replace("GUWAHATI","GUWAHATI(AS)")

dateWiseTable$Market =dateWiseTable$Market %>% str_replace("NAGPUR","NAGPUR(MS)")
dateWiseTable$Market =dateWiseTable$Market %>% str_replace("BHOPAL","BHOPAL(MP)")
dateWiseTable$Market =dateWiseTable$Market %>% str_replace("KOLKATA","KOLKATA(WB)")

dateWiseTable$Market =dateWiseTable$Market %>% str_replace("PATNA","PATNA(BHR)")
dateWiseTable$Market =dateWiseTable$Market %>% str_replace("SHIMLA","SHIMLA(HP)")
dateWiseTable$Market =dateWiseTable$Market %>% str_replace("CHANDIGARH","CHANDIGARH(PB)")


dateWiseTable$Market =dateWiseTable$Market %>% str_replace("JAIPUR","JAIPUR(RAJ)")

dateWiseTable$Market =dateWiseTable$Market %>% str_replace("LUCKNOW","LUCKNOW(UP)")

dateWiseTable =dateWiseTable %>% separate(Market,c('City','State1'),sep="\\(") %>% separate(State1,c('State'),sep="\\)")

#tableData$State=as.factor(tableData$State)
```
# Transform Data
Getting the top 10 for plotting

```{r transform data}

topStates=dateWiseTable %>% group_by(State) %>%
              summarise(quantity_state=sum(Arrival)) %>%
              arrange(desc(quantity_state))  %>% top_n(n=10)
#%>%
 #             filter(quantity_city > 2500000)
          
topStates          

```

# Explore Data
```{r explore }
library(ggplot2)
topstateplot=ggplot(topStates) +
    aes(reorder(State,quantity_state),weight=quantity_state)+
    geom_bar()+
      coord_flip()

library(plotly)

ggplotly(topstateplot)
```

```{r map plot}
library(ggmap)
topStates$State = topStates$State %>% str_replace("MS","Maharashtra")
topStates$State = topStates$State %>% str_replace("GUJ","Gujurat")
topStates$State = topStates$State %>% str_replace("KNT","karnataka")
topStates$State = topStates$State %>% str_replace("MP","MadhyaPradesh")
topStates$State = topStates$State %>% str_replace("RAJ","Rajasthan")
topStates$State = topStates$State %>% str_replace("WB","WestBengal")
topStates$State = topStates$State %>% str_replace("TN","TamilNadu")
topStates$State = topStates$State %>% str_replace("UP","UttarPradesh")
topStates$State = topStates$State %>% str_replace("TEL","Telangana")
topStates$State = topStates$State %>% str_replace("DEL","Delhi")
geo=geocode(topStates$State)
topStatesGeo = bind_cols(topStates,geo)
```
```{r scatter plot}
ggplot(topStatesGeo)+aes(lon,lat,size=quantity_state,color=State)+geom_point()

map <- get_map("India", zoom=5, maptype="toner-lite")
ggmap(map)+geom_point(data=topStatesGeo,aes(lon,lat,size=quantity_state,color=State))
```
```{r predicting price}
MSDATA= dateWiseTable %>% filter(State=="MS")

ggplot(MSDATA)+aes(NewDOA,MinPrice)+geom_line()
ggplot(MSDATA)+aes(NewDOA)+geom_line(aes(y=MinPrice))+geom_line(aes(y=MaxPrice),col="red")+geom_line(aes(y=Price),col="green")


MSDATAALL= MSDATA %>% gather("priceType","Price",5:7)

ggplot(MSDATAALL)+aes(NewDOA,Price,color=priceType)+geom_line()


```

# Model

```{r model}
ts = MSDATA %>% dplyr::select(NewDOA,Price)
colnames(ts)= c('ds','y')

library(prophet)

m= prophet(ts)

future = make_future_dataframe(m,period=3)
forecast=predict(m,future)
plot(m,forecast)


```

# communicate

